\documentclass[11pt]{article}
\usepackage[letterpaper, margin=1in, headheight=14pt, includeheadfoot]{geometry}
\usepackage{graphicx} % Required for inserting images
\graphicspath{ {/mnt/c/dev/} }
\usepackage{amssymb, amsfonts, amsmath}
\usepackage{multicol}
\usepackage{geometry}
\usepackage{tikz}
\usetikzlibrary{arrows,positioning,shapes,fit,calc}
% \usepackage{lmodern}
\usepackage[T1]{fontenc}
% \usepackage{ae}
% \usepackage{tgbonum}
% \usepackage{times}


\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancy}

% \fancyhf{}
\fancyfoot{} % clear all footer fields
\fancyhf[HLEO]{\textsc{shubhro gupta}}
\fancyhf[HCEO]{\textsc{comp201 - assignment 2}}
\fancyhf[HREO]{\emph{Page} \thepage \text{ }\emph{of} \pageref{LastPage}}
% \fancyhf[FREO]{Page \thepage\ of 5}
\renewcommand\headrulewidth{0pt}


\hfuzz=999pt
\hbadness=99999  % or any number >=10000

% \title{Comp 201 Assignment-1}
% \author{Shubhro Gupta}
% \date{Due Date: 7th September}

\begin{document}

% \maketitle




\section{Problem}
\emph{To Find. } 5-digit numbers such that either all their digits are even or all their digits are odd. \medskip \\
\emph{Claim. } The number of 5-digit numbers such that either all their digits are even or all their digits are odd is $5 \times 5^4$. \medskip \\
\emph{Proof. } Let $E$ be the set of 5-digit numbers such that all their digits are even and $O$ be the set of 5-digit numbers such that all their digits are odd.





\section{Problem}
\emph{Given. } A computer program takes as input binary codes of 5 bits and returns binary sequences of 4 bits. For every input, the program might either return an output or go into an infinite loop. We call a 5-bit input \emph{valid} if the program does not hang. Two programs are regarded as the same if they have the same set of valid inputs and return the same output for each valid input.

\subsection{Problem}
\emph{To Find. } The mathematical model of the above.

\subsection{Problem}
\emph{To Find. } The number of different programs that can be implemented. \medskip \\
\emph{Claim. } The number of different programs that can be implemented is $2^{16}$. \medskip \\
\emph{Proof. } Let $P$ be the set of all programs that can be implemented. Let $V$ be the set of all valid inputs. Let $O$ be the set of all outputs. Let $P_v$ be the set of all programs that return output for a valid input.




\section{Problem}
\emph{Given. } In a class of 40, 18 are into chess, 23 are into crosswords, and unknown $n$ are into quizzing. 7 are into both chess and quizzing. 9 are into both chess and quizzing. 4 students are into all the activities. \medskip \\
\emph{Claim. } The number of students into quizzing is 12.






\section{Problem}
\emph{To Find. } The number of ways in which 4 couples can be seated in a row of 8 seats if each couple wants to be seated together.





\section{Problem}
\emph{To Prove. } The number of solutions of $x_1 + x_2 + \cdots + x_k = n$ in non-negative integers is $C^{n+k−1}_n$.





\section{Problem}
\emph{Given. } A computer network with 10 distinct computers is set up such that each computer is connected to another computer. I want to determine the optimal way of sending a packet of information through the network so that it reaches every computer exactly once and returns to the starting computer.
\medskip \\
\emph{To Find. } The number of ways in which the packet can be sent.



\section{Problem} \emph{Done in Question 4.} \medskip \\




\section{Problem} \emph{To Prove. } That 2 points located on the circumference of a circle with a diameter of 6 cm, there exist two points with a distance of less than 2 cm between them.






\section{Problem} \emph{To Prove. } That $\sqrt{2}$ is irrational following these steps.
\begin{enumerate}
	\item Show that every rational number can be written as $\frac{p}{q}$, where p and q are relatively prime.
	\item Assume $\sqrt{2} = \frac{p}{q}$, where $p$ and $q$ are relatively prime, and prove that $p^2$ is even.
	\item Show that if $n^2$ is even, then $n$ is even.
	\item Use this to show that $p$ and $q$ are even, leading to a contradiction.
\end{enumerate}





\section{Problem} \emph{To Prove. } Every prime number greater than 3 is congruent to either 1 \emph{mod 6} or 5 \emph{mod 6}. \medskip \\


\section{Problem} \emph{To Prove. } If $n + 1$ distinct numbers are randomly selected, there exist two numbers whose remainder when divided by n is the same. \medskip \\


\section{Problem} \emph{To Prove. } Using modular arithmetic that $a + b$ is even, if $a$ and $b$ are odd integers. \medskip \\




\section{Problem}
\emph{To Find. } The digit at units place of $3^{101}$. \medskip \\
\emph{Claim. } The digit at units place of $3^{101}$ is 7. \medskip \\
\emph{Proof. } Let $n$ be the digit at units place of $3^{101}$. We know that $3^4 = 81$, and $3^{4n} = 1$, so $3^{100} = 1$. Therefore, $3^{101} = 3$. \medskip \\





\section{Problem}
\emph{To Write. } The PyRet code for the Euclidean algorithm and compute the greatest common divisor (GCD) of 124 and 284 using this algorithm by hand.

\end{document}
